\LARGE Untangling the link between traits, size and growth rate in plants

### 2016-07-28 ms.tex
Update build process, remove docker
- import build functions used in other papers

@@

@@

\subsubsection{Responisveness to light}

>>>>

Section 3.3 of King (2005) shows that the cost of turning over leaves, branches and fine roots may halve the height growth rate that could otherwise be attained.

King 1999 also predicts a change in the SLA optimising growth rate, via a cross correlation with self shading. Basically, the much greater path length from roots to leaves in trees vs. seedlings results in a much greater increment in support cost per increment in crown area for trees. This explanation is treated by the growth model of King (1999), which predicts that the SLA maximizing growth rate declines as seedlings grow larger, even before the onset of leaf turnover.

@@

(reich 1992, Niinements 2010, Gower-1993 - both show higher LAI in high LMA / long LL stands)

@@

\subsubsection{Responsiveness to light}
